Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-07-20 edubots_surveys.Rnw
Adding Hidden Phone Number feature description
Some corrections
Mainly grammar, but also qualifying "High school"

Initially, a single survey was developed for this purpose. Responses from 300 teachers were collected and analysed. This initial analysis led to the creation of a second survey, which collected responses from 200 different higher education teachers. The questions on this survey focus on discussing the implications and the impact of the development of future technology-enhanced tools and educational institutions’ policies by finding answers to the following research questions:

@@

The {\bf initial survey} was done in two separate Google forms, one for university and other for tertiary non-university teachers. Questions and responses were the same, except for the type of tertiary degrees that were taught. In both cases, we used mainly mailing lists, as well as Telegram groups, to spread the link to the form. The university form was spread in Spanish (mainly Andaluc\'{\i}a and Galicia) universities, and also Costa Rica and Mexico. The tertiary non-university teachers were mainly in Andaluc\'{\i}a. Dissemination and answers took place in the first quarter of 2021, post-pandemic and while, at least in Spain, many universities had mandatory virtual teaching.

A total of 282 teachers responded to the survey: 193 teaching at the University (68.4\%) and 89 at high school (31.6\%).

All surveys
% Antonio - I would say "The two surveys"
had the same common, initial questions for segmentation:\begin{itemize}
\item Degrees or titles where the teacher was working, either university or other tertiary education.
\item Discipline: Engineering, Social Sciences, Health and Bio, Sciences, Humanities, Other.
\item Gender: Man, Woman, Rather not say.
\item Age: 25-35, 35-45, 45-55, more than 55.
\item Experience on the job: up to 5 years, 5-15 years, 15-25 years, more than 25 years.
\item Type of degree: university, other tertiary education. This question was implicit in the first survey, since one and the other filled different forms, it was explicit in the second survey.
\end{itemize}

@@

\textit{3. Which media features do you value the most for your interaction with your students?}
\begin{itemize}
\item Familiarity with its use i.e. that I do not need to learn a new tool. [\texttt{Familiarity}]
\item The official formation/training provided by your institution on its use. [\texttt{Official formation}]
\item That only one-directional communication is allowed (from teachers to students). [\texttt{Unidirectionality}]
\item Non-hierarchical tools that allowed teacher-to-student and student-to-student communication. [\texttt{Horizontally}]
\item That allow additional functionalities such as interfaces to other tools. [\texttt{Connectivity}]
\item That allow teachers to develop/add their own functionalities (e.g. automatic correction tools). [\texttt{Pluggability}]
\item That let me avoid to worry about maintenance and that it is easily sustainable from one year to the next. [\texttt{Sustainability}]
\item That allow to extract data to assess the student performance. [\texttt{Analytics}]
% Antonio - Is it missing one feature concerning Hidden Phone Numer???
\end{itemize}

@@

Regarding Gender grouping, both gender agree in their uses, so it seems not relevant at all. When looking at the plot containing the sector differentiation it is interesting ot observe how university teachers prefer in a higher proportion to use them for grades and FAQs in comparison with Vocational/High School teachers. This seems reasonable as the frequency of seeing the students is smaller at the University so, automating the grade notification for continuous evaluation could seem much more comfortable using an automated tool than using the traditional platform. Furthermore, the high student/teacher ratios that university docents have to deal with could be another reason to have a higher number of them willing to use chatbots for FAQs. This could ameliorate the number of misunderstandings and email overload that so many students might generate.

>>>>

Initially, a single survey was developed for this purpose. Responses from 300 teachers were collected and analysed. An initial analysis of these responses led to the creation of a second survey, which collected responses from 200 different higher education teachers. The questions on this survey focus on discussing the implications and the impact of the development of future technology-enhanced tools and educational institutions’ policies by finding answers to the following research questions:

@@

The {\bf initial survey} was done in two separate Google forms, one for university and other for tertiary non-university teachers. Questions and responses were the same, except for the type of tertiary degrees that were taught. In both cases, we used mainly mailing lists, as well as Telegram groups, to spread the link to the form. The university form was spread in Spanish (mainly Andaluc\'{\i}a and Galicia) universities, and also Costa Rica and Mexico. The tertiary non-university teachers are based mainly in Andaluc\'{\i}a. Dissemination and answers took place in the first quarter of 2021, post-pandemic and while, at least in Spain, many universities had mandatory virtual teaching.

A total of 282 teachers responded to the survey: 193 teaching at the University (68.4\%) and 89 at other tertiary education institutions (31.6\%).

The surveys have the same common, initial questions for segmentation:\begin{itemize}
\item Degrees or titles where the teacher was working, either university or other tertiary education.
\item Discipline: Engineering, Social Sciences, Health and Bio, Sciences, Humanities, Other.
\item Gender: Man, Woman, Rather not say.
\item Age: 25-35, 35-45, 45-55, more than 55.
\item Experience on the job: up to 5 years, 5-15 years, 15-25 years, more than 25 years.
\item Type of degree: university, other tertiary education. This question was implicit in the first survey, since one and the other filled different forms, it was explicit in the second survey.
\end{itemize}

@@

\textit{3. Which media features do you value the most for your interaction with your students?}
\begin{itemize}
\item Familiarity with its use i.e. that I do not need to learn a new tool. [\texttt{Familiarity}]
\item The official formation/training provided by your institution on its use. [\texttt{Official formation}]
\item That only one-directional communication is allowed (from teachers to students). [\texttt{Unidirectionality}]
\item Non-hierarchical tools that allowed teacher-to-student and student-to-student communication. [\texttt{Horizontally}]
\item Connectivity to other tools, for instance common login. [\texttt{Connectivity}]
\item Possibility for teachers to develop/add their own functionalities (e.g. automatic correction tools). [\texttt{Pluggability}]
\item Possibility for users to hide personal data (such as my telephone number). [\texttt{Hidden Phone Number}]
\item Not having to worry about maintenance and that it is easily sustainable from one year to the next. [\texttt{Sustainability}]
\item That it offers the chance to extract data to assess the student performance. [\texttt{Analytics}]
\end{itemize}

@@

Regarding Gender grouping, both gender agree in their uses, so it seems not relevant at all. When looking at the plot containing the sector differentiation it is interesting ot observe how university teachers prefer in a higher proportion to use them for grades and FAQs in comparison with Vocational High School teachers. This seems reasonable as the frequency of seeing the students is smaller at the University so, automating the grade notification for continuous evaluation could seem much more comfortable using an automated tool than using the traditional platform. Furthermore, the high student/teacher ratios that university docents have to deal with could be another reason to have a higher number of them willing to use chatbots for FAQs. This could ameliorate the number of misunderstandings and email overload that so many students might generate.
